## R software practice

### 1. Choose 3 countrys and plot gdp vs Year
1. Spain
2. Kenya
3. Japan

```{r echo=FALSE}
library('reshape2')
library('ggplot2')
gDat<-read.delim("gapminderDataFiveYear.txt")
dat<-subset(gDat,c(country=="Spain"|country=="Kenya"|country=="Japan"))
ggplot(dat,aes(x=year,y=gdpPercap,color=country)) + geom_point(size=3)+ facet_wrap(~ country)
```

Japan and Spain have similar gdp. Kenya is really low.


### 2. Calculate mean, min and max of Expectance Life

Mean:
```{r echo=FALSE}
aggregate(lifeExp~country, dat, FUN=mean)
```

Min:
```{r echo=FALSE}
aggregate(lifeExp~country, dat, FUN=min)
```

Max:
```{r echo=FALSE}
aggregate(lifeExp~country, dat, FUN=max)
```

Kenya's expectation life is lower than Japan and Spain that both are similar


### 3. Histograms

Histogram of Life Expectancy for all countrys

```{r echo=FALSE}
ggplot(gDat,aes(x=lifeExp)) + geom_histogram(binwidth=5)
```

Histogram of Life Expectancy for all countrys with a much narrower bandwith

```{r echo=FALSE}
ggplot(gDat,aes(x=lifeExp)) + geom_histogram(binwidth=1)
```

With narrower bandwith some hidden pattern can appear
